%\par{
%Sono un informatico laureato alla
%triennale di informatica all’universit\`a
%di Bologna. Catturato fin da subito
%dalla system administration, ho
%coltivato in questi anni di studio la
%mia passione svolgendo attivit\`a di
%sistemista presso un’associazione no
%profit studentesca (ADMstaff) dove ho
%gestito, insieme ad altri studenti, una
%piccola rete di server.
%Mi sono dedicato inoltre durante i miei studi allo sviluppo
%e la manutenzione di applicazioni web, privilegiando il lato Back-end.
%Infine negli ultimi anni della triennale mi sono
%avvicinato al tema della sicurezza delle reti,
%che \`e stato poi il tema principale del mio lavoro di tesi.
%}

\par{
I am a Computer Science Master student at the EIT Digital Master School enrolled in the double degree Cybersecurity track. I attended the first year in the University of Trento with the specialization in \textit{Security and Privacy} and I am now attending the second year at EURECOM in Nice where I am spacializing in \textit{Mobile and Cloud Security}.
I was captured since the beginning of my career by the field of System and Network Administration,
 and I cultivated this passion during my years of study. I graduated in Bologna in 2018 with a thesis on security of large networked systems. During the bachelor I volunteered in a student
group called ADMStaff, where I deployed and maintained together with other students a small network of
servers which offer Best Effort services to other CS students.
I also developed and maintained web applications, mostly focusing on the Back-end layer.
Between the bachelor and the master I did a specialization course on .NET programming and I worked for a few months as a System and Network administrator at NetService. There I provided consultancy about security posture of the company and deployed the company's Security Event Manager. 
During the year in Trento I attended both technical and business couses and became familiar with security issues but also with the concepts of Business Modelling and Customer Validation. 
}
