\sectionTitle{Educational experiences}{\faMortarBoard}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
  {May 2018}   {.NET Development Course}{OverNet Education}{Bologna, Italy}
  {Jun 2018} {
                    Technical course on .NET framework, C\# and MSSQL databases
                  }
                  {\textbf{MSSQL}, TSQL, \textbf{C\#}, .NET , Agile, \textbf{TDD}, git, SQL Server Management Studio, OO, Entity Framework, LINQ, MVC, WPF}
\emptySeparator
  \experience
    {Sep 2017}   {Analysis of an Intrusion Detection System based on Packet Sampling}{BSc Dissertation}{University of Bologna}
    {Mar 2018} {
                      Performance evaluation of a monitoring system which combines the sFlow sampling technology with the IDS Suricata.
                    }
                    {Linux, \textbf{Networks}, sFlow, NetFlow, Elasticsearch, Kibana, C, \textbf{Python}, Bash}
  \emptySeparator
  \experience
    {Sep 2016}   {System Administration}{AdmStaff}{University of Bologna}
    {Mar 2018} {
                      Administration of a small network of servers offering BES services to other CS students. \linebreak
                      Hands-on experience regarding installation and maintenance of several Open Source software.
                    }
                    {\textbf{Linux}, Networks, Postfix, BIND DNS, GitLab CE, LDAP, NFS, 802.1x, Radius}
  \emptySeparator
  \experience
    {}   {University Projects}{}{}
    {} {
                  \begin{itemize}
                    \item Development of a kernel for the Kaya operating system, an Open Source project for the ARMv7 architecture.
                    \item Development of a web platform for the paper revision in scientific conferences.
                    % \item Development of a browser plugin to calculate HTML page metrics in order to study effectivenes of Page Object design pattern. 
                    \item Static Analysis of programs to detect and demonstrate exploitability of XSS attacks on static HTML pages.
                    \item Development of a smart monitoring device aimed for office wellbeing. Marketing analysis and customer validation of the product.
                    \item Study and experimentation with the security orchestrator The Hive, the threat information sharing platform MISP and the investigation and response tool Cortex.
                    \item Study and Risk Assessment for an Unmanned Aerial Service Traffic Management (UTM) with the SECRAM framework
                  \end{itemize}
                }
                  {C, Linux Kernel, Python, MongoDB, Flask, REST, Angular, \textbf{Java}, Javascript, \textbf{Business}, The Hive, Security, Risk Assessment }
  \emptySeparator
\end{experiences}
